---
title: "NOIS"
author: "Hoang Tran"
date: "5/9/2017"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## NOIS

Non-Parametric Outlier Identification and Smoothing.

This package implements outlier identification and smoothing for non-linear and time series data.

## Installation

```{r, eval=FALSE}
install.packages('devtools')
devtools::install_github('hoangtt1989/NOIS')
library(NOIS)
```


## Simulated Data Example

We generate a random sine curve and perturb it with outliers.

```{r}
library(ggplot2)
set.seed(123)
npts <- 200
nout <- floor(.1*npts)

xt <- seq(from=0, to=2*pi, length.out=npts)
gaussnoise <- rnorm(npts)

outliers <- sample(floor(npts/2):npts, size=nout)
randpts <- runif(nout, min=5, max=7)
yt <- sin(xt) + gaussnoise
yt[outliers] <- yt[outliers] + randpts
xt_outliers = xt[outliers]

orig_func <- sin(xt)
data <- data.frame(x = xt, y = yt, true_outlier = xt %in% xt_outliers)

ggplot(data) + geom_point(aes(x, y, color = true_outlier))
```

We use NOIS to detect outliers and estimate the underlying curve.

```{r}
sine_fit <- NOIS_fit(data, CV_method = 'LOOCV', pool_q = nout)
sine_fit
```

We plot the estimated curve and mark the detected outliers. NOIS correctly detects all of the outliers.

```{r}
outlier_plot(sine_fit)
```
